\let\textcircled=\pgftextcircled
\chapter{W BOSON PRODUCTION IN PROTON-LEAD COLLISIONS} \label{sec:WBoson}

% INTRODUCTION OF CHAPTER

This chapter describes the measurement of the production of \W bosons in proton-lead (\pPb) collisions at a nucleon-nucleon center-of-mass energy $\sqrtsnn = 8.16$~\TeV with the CMS detector. As mentioned in \sect{sec:Introduction_Physics}, the primary processes that contribute at LHC energies to the production of \W bosons are $\cPqu \cPaqd \rightarrow \Wp$ and $\cPqd \cPaqu \rightarrow \Wm$. Once produced, \W bosons can decay weakly to either leptons or quarks. The semi-muonic decay (\WToMuNu) is of particular interest, since muons lose negligible energy in the medium and the surrounding background is small.

The individual \Wp and \Wm production rates are expected to be modified relative to proton-proton (\pp) collisions, due to the different content of up and down quarks in the proton compared to the lead nuclei. The distribution of partons inside the nuclei can also be modified by parton shadowing (or depletion), which can alter the \W boson yields at the LHC. Precise measurements of \W production in \pPb collisions can therefore provide strong constrains to the nuclear parton distribution functions (nPDF).

The analysis is currently been reviewed. Previous results have been published by the CMS collaboration on \pPb data at $\sqrtsnn = 5.02$~\TeV collected in 2013 \cite{HIN-13-007}. A similar study has been performed by the ALICE~\cite{ALICE_pPb_W_5TeV} and the ATLAS~\cite{ATLAS_pPb_W_5TeV} collaborations at \pPb collision energies of 5.02~\TeV.

The datasets and simulated samples are described in \sect{sec:WBoson_Samples}. In \sect{sec:WBoson_EventSelection}, the event selection is presented. The relevant backgrounds are introduced in \sect{sec:WBoson_Background}. Finally, the systematic uncertainties are discussed in \sect{sec:WBoson_SystematicUncertainties} and the results are detailed in \sect{sec:WBoson_Results}.

% SECTIONS OF CHAPTER

\input{Chapters/Main/WBoson/Sections/Theory}

\clearpage

%\input{Chapters/Main/WBoson/Sections/Samples}

%\input{Chapters/Main/WBoson/Sections/Selection}

%\input{Chapters/Main/WBoson/Sections/Corrections}

%\input{Chapters/Main/WBoson/Sections/Efficiency}

%\input{Chapters/Main/WBoson/Sections/SignalExtraction}

%\input{Chapters/Main/WBoson/Sections/Systematics}

\clearpage

\input{Chapters/Main/WBoson/Sections/Results}


% END OF CHAPTER
\clearpage
